---
title: "Phase 2: Firm-Level Difference-in-Differences"
execute:
  cache: false
---

```{r}
#| label: setup
#| cache: false
#| include: false

rm(list = ls())
gc()

pacman::p_load(
  targets,
  tidyverse,
  did,
  tinytable,
  patchwork,
  here,
  labelled
)

here::i_am("notebooks/did.qmd")
tar_config_set(store = here("_targets"))

source(here("R/did.R"))

theme_set(theme_minimal(base_size = 13))

```


```{r}
# Load targets
did_data_cit  <- tar_read(did_data_cit)
did_data_pit  <- tar_read(did_data_pit)
did_summaries <- tar_read(did_summaries)
```

```{r}
#| label: helpers
#| cache: false
#| include: false

# Extract pre-trend coefficients from event-study summary data
extract_pretrend <- function(es_data) {
  es_data |>
    filter(e < 0, !is.na(se)) |>
    mutate(
      lower = att - 1.96 * se,
      upper = att + 1.96 * se,
      sig   = if_else(lower > 0 | upper < 0, "yes", "")
    )
}

# Build a titled event-study plot from did_summaries for a given block_id
did_es_plot <- function(bid, did_summaries, title_prefix = NULL) {
  row <- did_summaries |> filter(block_id == bid)
  if (nrow(row) == 0) return(NULL)

  outcomes  <- did_outcomes()
  label <- outcomes[[row$outcome]]$label
  title <- if (!is.null(title_prefix)) paste(title_prefix, "-", label) else label
  plot_did_event_study(row$event_study[[1]], row$event_study_crit_val, title)
}

# Compose a patchwork panel of event-study plots for one region
# Layout: rows = outcomes, col 1 = CIT, col 2 = PIT
build_region_es_panel <- function(scope, did_summaries) {
  outcomes <- did_outcomes()
  tx_labels <- c(cit = "CIT", pit = "PIT")

  plots <- purrr::map(names(outcomes), \(out_id) {
    purrr::map(c("cit", "pit"), \(tx) {
      bid <- paste(scope, tx, out_id, sep = "_")
      p <- did_es_plot(bid, did_summaries, title_prefix = tx_labels[[tx]])
      if (is.null(p)) p <- patchwork::plot_spacer()
      p
    })
  }) |> purrr::list_c()

  patchwork::wrap_plots(plots, ncol = 2)
}

# Forest plot: overall ATT by region and outcome, faceted by treatment
plot_did_coef <- function(did_summaries) {
  outcomes <- did_outcomes()
  tx_labels <- c(cit = "CIT", pit = "PIT")

  df <- did_summaries |>
    filter(scope %in% c("EAP", "MIC", "HIC")) |>
    mutate(
      outcome_label = purrr::map_chr(outcome, \(o) outcomes[[o]]$label),
      tx_label = tx_labels[tx],
      lower = overall_att - 1.96 * overall_se,
      upper = overall_att + 1.96 * overall_se
    )

  ggplot(df, aes(x = overall_att, y = outcome_label, color = scope)) +
    geom_vline(xintercept = 0) +
    geom_pointrange(aes(xmin = lower, xmax = upper),
                    position = position_dodge(width = 0.5),
                    size = 0.4,
                    alpha = 0.6
                    ) +
    facet_wrap(~ tx_label) +
    labs(x = "ATT", y = NULL, color = "Region") +
    theme_minimal(base_size = 13) +
    theme(legend.position = "bottom")
}

# Regional spaghetti: one line per region with ±1 SE ribbon
plot_regional_spaghetti <- function(data, outcome_var, label) {
  agg <- data |>
    filter(!is.na(region), !is.na(.data[[outcome_var]])) |>
    group_by(region, year) |>
    summarise(
      mean = mean(.data[[outcome_var]], na.rm = TRUE),
      se   = sd(.data[[outcome_var]], na.rm = TRUE) / sqrt(n()),
      .groups = "drop"
    ) |>
    mutate(region = factor(region, levels = c("EAP", "MIC", "HIC")))

  ggplot(agg, aes(x = year, y = mean, color = region, fill = region)) +
    geom_ribbon(aes(ymin = mean - se, ymax = mean + se), alpha = 0.15, linewidth = 0) +
    geom_line(linewidth = 0.8) +
    scale_color_brewer(palette = "Set2", name = "Region") +
    scale_fill_brewer(palette = "Set2", guide = "none") +
    labs(x = "Year", y = label) +
    theme(legend.position = "bottom") +
    scale_x_continuous(breaks = seq(2006, 2018, 2))
}

# Regional spaghetti with log10 scale: plots raw Y, log-scaled axis
plot_regional_spaghetti_log10 <- function(data, outcome_var, label) {
  agg <- data |>
    filter(!is.na(region), !is.na(.data[[outcome_var]]),
           .data[[outcome_var]] > 0) |>
    group_by(region, year) |>
    summarise(
      mean = mean(.data[[outcome_var]], na.rm = TRUE),
      se   = sd(.data[[outcome_var]], na.rm = TRUE) / sqrt(n()),
      .groups = "drop"
    ) |>
    mutate(region = factor(region, levels = c("EAP", "MIC", "HIC")))

  ggplot(agg, aes(x = year, y = mean, color = region, fill = region)) +
    geom_ribbon(aes(ymin = mean - se, ymax = mean + se), alpha = 0.15, linewidth = 0) +
    geom_line(linewidth = 0.8) +
    scale_y_log10(labels = scales::label_comma()) +
    scale_color_brewer(palette = "Set2", name = "Region") +
    scale_fill_brewer(palette = "Set2", guide = "none") +
    labs(x = "Year", y = label) +
    theme(legend.position = "bottom") +
    scale_x_continuous(breaks = seq(2006, 2018, 2))
}

# Regional spaghetti indexed to 2006 = 100
plot_regional_spaghetti_indexed <- function(data, outcome_var, label) {
  agg <- data |>
    filter(!is.na(region), !is.na(.data[[outcome_var]]),
           .data[[outcome_var]] > 0) |>
    group_by(region, year) |>
    summarise(
      mean = mean(.data[[outcome_var]], na.rm = TRUE),
      se   = sd(.data[[outcome_var]], na.rm = TRUE) / sqrt(n()),
      .groups = "drop"
    ) |>
    group_by(region) |>
    mutate(
      base = mean[year == 2006],
      index = mean / base * 100,
      index_se = se / base * 100
    ) |>
    ungroup() |>
    mutate(region = factor(region, levels = c("EAP", "MIC", "HIC")))

  ggplot(agg, aes(x = year, y = index, color = region, fill = region)) +
    geom_ribbon(aes(ymin = index - index_se, ymax = index + index_se),
                alpha = 0.15, linewidth = 0) +
    geom_line(linewidth = 0.8) +
    geom_hline(yintercept = 100, linetype = "dashed", alpha = 0.4) +
    scale_color_brewer(palette = "Set2", name = "Region") +
    scale_fill_brewer(palette = "Set2", guide = "none") +
    labs(x = "Year", y = paste0(label, " (2006 = 100)")) +
    theme(legend.position = "bottom") +
    scale_x_continuous(breaks = seq(2006, 2018, 2))
}

# Country spaghetti (EAP only): one line per country with treatment vlines
plot_country_spaghetti <- function(data, outcome_var, label) {
  country_means <- data |>
    filter(region == "EAP", !is.na(.data[[outcome_var]])) |>
    group_by(ccode, country, year) |>
    summarise(
      mean = mean(.data[[outcome_var]], na.rm = TRUE),
      se   = sd(.data[[outcome_var]], na.rm = TRUE) / sqrt(n()),
      .groups = "drop"
    )

  # Gather treatment years from both CIT and PIT
  treat_years <- bind_rows(
    did_data_cit |>
      distinct(ccode, country, first_treated_year) |>
      mutate(tax = "CIT"),
    did_data_pit |>
      distinct(ccode, country, first_treated_year) |>
      mutate(tax = "PIT")
  ) |>
    filter(first_treated_year > 0) |>
    semi_join(country_means, by = "ccode")

  ggplot(country_means, aes(x = year, y = mean, color = country, fill = country)) +
    geom_ribbon(aes(ymin = mean - se, ymax = mean + se), alpha = 0.15, linewidth = 0) +
    geom_line(linewidth = 0.6) +
    geom_vline(
      data = treat_years,
      aes(xintercept = first_treated_year, linetype = tax),
      alpha = 0.4
    ) +
    scale_linetype_manual(values = c(CIT = "solid", PIT = "dashed"), name = "Tax cut") +
    labs(x = "", y = label, color = "Country") +
    theme(legend.position = "bottom") +
    facet_wrap(~country, ncol = 2) +
    guides(color = "none", fill = "none") +
    scale_y_log10(labels = scales::label_comma())
}

# Regional event-time spaghetti: one line per region, treated units only
plot_regional_event_spaghetti <- function(data, outcome_var, label) {
  agg <- data |>
    filter(first_treated_year > 0, !is.na(region), !is.na(.data[[outcome_var]])) |>
    mutate(event_time = year - first_treated_year) |>
    group_by(region, event_time) |>
    summarise(
      mean = mean(.data[[outcome_var]], na.rm = TRUE),
      se   = sd(.data[[outcome_var]], na.rm = TRUE) / sqrt(n()),
      .groups = "drop"
    ) |>
    mutate(region = factor(region, levels = c("EAP", "MIC", "HIC")))

  ggplot(agg, aes(x = event_time, y = mean, color = region, fill = region)) +
    geom_ribbon(aes(ymin = mean - se, ymax = mean + se), alpha = 0.15, linewidth = 0) +
    geom_line(linewidth = 0.8) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.5) +
    scale_color_brewer(palette = "Set2", name = "Region") +
    scale_fill_brewer(palette = "Set2", guide = "none") +
    labs(x = "Event time (years relative to tax cut)", y = label) +
    theme(legend.position = "bottom") +
    scale_y_log10(labels = scales::label_comma())
}

# Country event-time spaghetti (EAP only): one line per country, treated only
plot_country_event_spaghetti <- function(data, outcome_var, label) {
  country_means <- data |>
    filter(region == "EAP", first_treated_year > 0, !is.na(.data[[outcome_var]])) |>
    mutate(event_time = year - first_treated_year) |>
    group_by(ccode, country, event_time) |>
    summarise(
      mean = mean(.data[[outcome_var]], na.rm = TRUE),
      se   = sd(.data[[outcome_var]], na.rm = TRUE) / sqrt(n()),
      .groups = "drop"
    )

  ggplot(country_means, aes(x = event_time, y = mean, color = country, fill = country)) +
    geom_ribbon(aes(ymin = mean - se, ymax = mean + se), alpha = 0.15, linewidth = 0) +
    geom_line(linewidth = 0.6) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.5) +
    labs(x = "Event time (years relative to tax cut)", y = label, color = "Country") +
    theme(legend.position = "bottom") +
    guides(fill = "none") +
    scale_y_log10(labels = scales::label_comma())
}

# Summary table builder for any scope (consumes did_summaries tibble)
build_did_summary_table <- function(scope_prefix, did_summaries) {
  treatments <- did_treatments()
  outcomes   <- did_outcomes()
  tx_labels  <- c(cit = "CIT", pit = "PIT")

  scope_data <- did_summaries |> filter(scope == scope_prefix)

  summary_rows <- purrr::map_dfr(names(treatments), \(tx) {
    cells <- purrr::map(names(outcomes), \(out) {
      row <- scope_data |> filter(.data$tx == .env$tx, outcome == out)
      if (nrow(row) == 0) {
        return(list(att = NA_real_, se = NA_real_, n = NA_integer_))
      }
      list(att = row$overall_att, se = row$overall_se, n = row$n, wpval = row$wpval)
    }) |> setNames(names(outcomes))

    tibble(
      ` ` = c(tx_labels[[tx]], "", "Observations", "Pre-trends p"),
      row_type = c("att", "se", "n", "wpval"),
      !!!purrr::imap(cells, \(c, out_id) {
        if (is.na(c$att)) return(rep("—", 4))
        c(sprintf("%.3f", c$att),
          sprintf("(%.3f)", c$se),
          scales::comma(c$n),
          sprintf("%.3f", c$wpval))
      })
    ) |>
      rename(!!!setNames(names(outcomes), purrr::map_chr(outcomes, "label")))
  })

  n_tx <- length(treatments)
  n_rows_per_tx <- 4L
  panel_rows <- seq(n_rows_per_tx, (n_tx - 1) * n_rows_per_tx, by = n_rows_per_tx)
  se_rows    <- seq(2L, n_tx * n_rows_per_tx, by = n_rows_per_tx)

  summary_rows |>
    select(-row_type) |>
    tt() |>
    style_tt(i = se_rows,    line = "b", line_color = "gray") |>
    style_tt(i = panel_rows, line = "b", line_color = "black")
}
```

## Research design

Absorbing binary treatment: once a country cuts taxes, it stays treated forever. Countries with multiple tax cut episodes are assigned the **first** episode as the treatment date; subsequent cuts are subsumed into the post-treatment period. The `did` package [@callaway2021] handles staggered adoption and provides group-time ATTs with built-in pre-trend diagnostics.

Countries with multiple tax cut episodes: Take first episode as absorbing treatment.

- **Panel window**: 2006--2017 (balanced; firms observed in all 12 years)
- **Control group**: not-yet-treated
- **Base period**: universal
- **Covariates**: none (unconditional)
- **Outcomes**: log-transformed (log investment, log employment)


$$
Y_{it}=\beta T_{it} + \alpha_i + \delta_t + \varepsilon_{it}
$$


## Data

### Treatment summary

```{r}
#| label: fig-treatment-summary
#| fig-cap: "Countries by first treatment year and region"

bind_rows(
  did_data_cit |>
    distinct(ccode, first_treated_year, region) |>
    mutate(treatment = "CIT"),
  did_data_pit |>
    distinct(ccode, first_treated_year, region) |>
    mutate(treatment = "PIT")
) |>
  filter(!is.na(region)) |>
  mutate(
    year_label = if_else(
      first_treated_year == 0, "Never\ntreated",
      as.character(first_treated_year)
    ),
    region = factor(region, levels = c("EAP", "MIC", "HIC"))
  ) |>
  ggplot(aes(x = year_label, fill = region)) +
  geom_bar() +
  facet_wrap(~treatment) +
  scale_fill_brewer(palette = "Set2", name = "Region") +
  labs(x = "First treatment year", y = "Number of countries") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8), legend.position = "bottom")
```



```{r}
#| label: tbl-regional-stats
#| tbl-cap: "Panel composition by region"

bind_rows(
  did_data_cit |> mutate(treatment = "CIT"),
  did_data_pit |> mutate(treatment = "PIT")
) |>
  filter(!is.na(region)) |>
  group_by(treatment, region) |>
  summarise(
    countries       = n_distinct(ccode),
    firms           = n_distinct(firm_id),
    n_treated       = n_distinct(ccode[first_treated_year > 0]),
    share_treated   = n_treated / countries,
    median_treat_yr = median(
      unique(first_treated_year[first_treated_year > 0]), na.rm = TRUE
    ),
    .groups = "drop"
  ) |>
  mutate(
    share_treated   = sprintf("%.0f%%", share_treated * 100),
    median_treat_yr = if_else(is.na(median_treat_yr), "—", as.character(median_treat_yr))
  ) |>
  select(
    Treatment = treatment, Region = region,
    Countries = countries, Firms = firms,
    Treated = n_treated, `Share treated` = share_treated,
    `Median treat year` = median_treat_yr
  ) |>
  tt()
```

### Raw outcome trends

```{r}
#| label: fig-outcome-boxplots
#| fig-cap: "Distribution of outcome variables by region. Log scale, 2016."
#| fig-alt: "Mean firm in each region"
did_data_cit |>
  filter(year == max(year), !is.na(region)) |>
  select(region, `Investments (USD)` = investments, Employees = employees) |>
  pivot_longer(!region) |>
  # mutate(name = str_to_title(name)) |>
  ggplot(aes(region, value, fill = region)) +
  geom_boxplot(alpha = 0.6) +
  facet_wrap(~name, scales = "free_y") +
  scale_y_log10(labels = scales::label_comma()) +
  labs(
    x = "",
    y = ""
  ) +
  theme(legend.position = "none")

```


```{r}
#| label: tbl-summarys-stats
#| tbl-cap: Summary statistics. Firm-level data. 2016.

dict <- generate_dictionary(did_data_cit) |>
  as_tibble() |>
  select(
    name = variable,
    label
  )

did_data_cit |>
  filter(year == max(year), !is.na(region)) |>
  select(!c(ccode, country, year, firm_id, first_treated_year, treated, region, firm_id_num)) |>
  select(!starts_with("t_")) |>
  pivot_longer(everything()) |>
  summarise(
    .by = name,
    N = sum(!is.na(value)),
    Mean = mean(value, na.rm = T),
    Median = median(value, na.rm = T),
    `Std.Dev.` = sd(value, na.rm = T),
    Min = min(value, na.rm = T),
    Max = max(value, na.rm = T)
  ) |>
  left_join(dict) |>
  select(-name) |>
  select(Variable = label, everything()) |>
  mutate(across(where(is.numeric), \(x) scales::number(x, big.mark = ",", accuracy = 1))) |>
  tt() |>
  style_tt(j = 1, align = "l") |>
  style_tt(j = 2:7, align = "r")

```


::: {#fig-region-trends-log10 layout-ncol="1"}

```{r}
#| label: fig-regional-investment-log10
#| fig-cap: "Investment"
#| fig-height: 4
plot_regional_spaghetti_log10(did_data_cit, "investments", "Investment (USD)")
```

```{r}
#| label: fig-regional-employment-log10
#| fig-cap: "Employment"
#| fig-height: 4
plot_regional_spaghetti_log10(did_data_cit, "employees", "Employees")
```

Firm-level mean outcome by region, log scale (± 1 SE)
:::

::: {#fig-region-trends-indexed layout-ncol="1"}

```{r}
#| label: fig-regional-investment-indexed
#| fig-cap: "Investment"
#| fig-height: 4
plot_regional_spaghetti_indexed(did_data_cit, "investments", "Investment") +
  scale_y_continuous(breaks = seq(100, 900, 200))
```

```{r}
#| label: fig-regional-employment-indexed
#| fig-cap: "Employment"
#| fig-height: 4
plot_regional_spaghetti_indexed(did_data_cit, "employees", "Employment") +
  scale_y_continuous(breaks = seq(100, 200, 25))
```

Firm-level mean outcome growth by region, indexed to 2006 = 100 (± 1 SE)
:::


::: {#fig-country-trends layout-ncol="1"}
```{r}
#| label: fig-eap-investment
#| fig-cap: "Investment"
#| fig-height: 8

plot_country_spaghetti(did_data_cit, "investments", "Investment (USD)")
```

```{r}
#| label: fig-eap-employment
#| fig-cap: "Employment"
#| fig-height: 8

plot_country_spaghetti(did_data_cit, "employees", "Employees")
```

Firm-level mean outcomes by country along with tax cut episodes, South East Asia (± 1 SE, log scale)
:::


### Event-time trends

Raw means on event time for CIT-treated countries. Event time 0 marks the year of the tax cut.

::: {#fig-region-event-trends layout-ncol="2"}
```{r}
#| label: fig-regional-event-investment-cit
#| fig-cap: "CIT, Investment"
#| fig-height: 5
plot_regional_event_spaghetti(did_data_cit, "investments", "Investment (USD)")
```

```{r}
#| label: fig-regional-event-investment-pit
#| fig-cap: "PIT, Investment"
#| fig-height: 5
plot_regional_event_spaghetti(did_data_pit, "investments", "Investment (USD)")
```

```{r}
#| label: fig-regional-event-employment-cit
#| fig-cap: "CIT, Employment"
#| fig-height: 5
plot_regional_event_spaghetti(did_data_cit, "employees", "Employment")
```

```{r}
#| label: fig-regional-event-employment-pit
#| fig-cap: "PIT, Employment"
#| fig-height: 5
plot_regional_event_spaghetti(did_data_pit, "employees", "Employment")
```

Firm-level mean outcomes by region on event time (± 1 SE, log scale). Treated countries only.
:::


::: {#fig-country-event-trends layout-ncol="2"}
```{r}
#| label: fig-eap-event-investment-cit
#| fig-cap: "CIT, Investment"
#| fig-height: 5
plot_country_event_spaghetti(did_data_cit, "investments", "Investment (USD)")
```


```{r}
#| label: fig-eap-event-investment-pit
#| fig-cap: "PIT, Investment"
#| fig-height: 5
plot_country_event_spaghetti(did_data_pit, "investments", "Investment (USD)")
```

```{r}
#| label: fig-eap-event-employment-cit
#| fig-cap: "CIT, Employment"
#| fig-height: 5
plot_country_event_spaghetti(did_data_cit, "employees", "Employment")
```


```{r}
#| label: fig-eap-event-employment-pit
#| fig-cap: "PIT, Employment"
#| fig-height: 5
plot_country_event_spaghetti(did_data_pit, "employees", "Employment")
```

Firm-level mean outcomes by country on event time (± 1 SE, log scale). South East Asia treated only.
:::

## Results

### World ATT

::: {#fig-did-cit-event-studies}

```{r}
#| fig-height: 4
#| layout-ncol: 2

for (out_id in names(did_outcomes())) {
  bid <- paste("world", "cit", out_id, sep = "_")
  p <- did_es_plot(bid, did_summaries)
  if (!is.null(p)) print(p)
}
```

Event-study: CIT cut effects on firm-level outcomes
:::



::: {#fig-did-pit-event-studies}

```{r}
#| fig-height: 4
#| layout-ncol: 2

for (out_id in names(did_outcomes())) {
  bid <- paste("world", "pit", out_id, sep = "_")
  p <- did_es_plot(bid, did_summaries)
  if (!is.null(p)) print(p)
}
```

Event-study: PIT cut effects on firm-level outcomes
:::


```{r}
#| label: tbl-did-summary
#| tbl-cap: "Overall ATT estimates"

build_did_summary_table("world", did_summaries)
```


At the whole world level, there is little to say about the causal effect of tax cuts on firm-level results. Overall, parallel pre-trends do not hold. A reason this may happen is because of the endogeneity with which tax cuts may happen; fiscal policy may be responding to a particular economic environment, which is itself a lack of parallel pre-trends.

### Region level ATT

```{r}
#| label: fig-did-regional-coef
#| fig-cap: "Overall ATT by region and outcome"
#| fig-height: 6

plot_did_coef(did_summaries)
```

```{r}
#| label: fig-did-eap-es
#| fig-cap: "East Asian Countries"
#| fig-height: 36
#| fig-width: 10

build_region_es_panel("EAP", did_summaries)
```

```{r}
#| label: fig-did-mic-es
#| fig-cap: "Middle Income Countries"
#| fig-height: 36
#| fig-width: 10

build_region_es_panel("MIC", did_summaries)
```

```{r}
#| label: fig-did-hic-es
#| fig-cap: "High Income Countries"
#| fig-height: 36
#| fig-width: 10

build_region_es_panel("HIC", did_summaries)
```

::: {#tbl-region-att .column-body-outset}

```{r}
#| label: tbl-region-att-eap
#| tbl-cap: "East Asian Countries"
build_did_summary_table("EAP", did_summaries)
```

```{r}
#| label: tbl-region-att-mic
#| tbl-cap: "Middle Income Countries"
build_did_summary_table("MIC", did_summaries)
```

```{r}
#| label: tbl-region-att-hic
#| tbl-cap: "High Income Countries"
build_did_summary_table("HIC", did_summaries)
```

Regional ATT estimates
:::


### References