---
title: "Phase 2: Firm-Level Difference-in-Differences"
---

```{r}
#| label: setup
#| cache: false
#| include: false

rm(list = ls())
gc()

pacman::p_load(
  targets,
  tidyverse,
  did,
  tinytable,
  here
)

here::i_am("notebooks/did.qmd")
tar_config_set(store = here("_targets"))

source(here("R/did.R"))

theme_set(theme_minimal(base_size = 13))

# Load targets
did_data_cit <- tar_read(did_data_cit)
did_data_pit <- tar_read(did_data_pit)
did_models   <- tar_read(did_models)
did_results  <- tar_read(did_results)
did_plots    <- tar_read(did_plots)
```

```{r}
#| label: helpers
#| cache: false
#| include: false

# Extract pre-trend coefficients from event-study aggregation
extract_pretrend <- function(aggte_obj) {
  es <- data.frame(
    e   = aggte_obj$egt,
    att = aggte_obj$att.egt,
    se  = aggte_obj$se.egt
  ) |>
    filter(e < 0, !is.na(se)) |>
    mutate(
      lower = att - 1.96 * se,
      upper = att + 1.96 * se,
      sig   = if_else(lower > 0 | upper < 0, "yes", "")
    )
  es
}
```

## Design

Absorbing binary treatment: once a country cuts taxes, it stays treated forever. The `did` package (Callaway & Sant'Anna 2021) handles staggered adoption and provides group-time ATTs with built-in pre-trend diagnostics.

- **Panel window**: 2006--2017 (balanced; firms observed in all 12 years)
- **Control group**: not-yet-treated
- **Base period**: universal
- **Covariates**: none (unconditional)
- **Outcomes**: log-transformed (log investment, log employment)

## Treatment summary

```{r}
#| label: tbl-treatment-summary

bind_rows(
  did_data_cit |>
    distinct(ccode, first_treated_year) |>
    mutate(treatment = "CIT"),
  did_data_pit |>
    distinct(ccode, first_treated_year) |>
    mutate(treatment = "PIT")
) |>
  mutate(
    status = if_else(first_treated_year == 0, "Never treated", as.character(first_treated_year))
  ) |>
  count(treatment, status) |>
  pivot_wider(names_from = treatment, values_from = n, values_fill = 0) |>
  arrange(status) |>
  tt(caption = "Countries by first treatment year")
```


## Corporate Income Tax (CIT)

::: {#fig-did-cit layout-ncol=2}

```{r}
#| label: fig-did-cit-investments
#| fig-cap: "Investment"
did_plots$cit_investments
```

```{r}
#| label: fig-did-cit-employees
#| fig-cap: "Employment"
did_plots$cit_employees
```

Event-study: effect of CIT cuts on firm-level outcomes
:::

```{r}
#| label: tbl-did-cit-att

tibble(
  Outcome = c("log(Investment)", "log(Employment)"),
  ATT = c(
    did_results$cit_investments$overall$overall.att,
    did_results$cit_employees$overall$overall.att
  ),
  SE = c(
    did_results$cit_investments$overall$overall.se,
    did_results$cit_employees$overall$overall.se
  )
) |>
  mutate(
    `95% CI` = paste0(
      "[", sprintf("%.3f", ATT - 1.96 * SE), ", ",
      sprintf("%.3f", ATT + 1.96 * SE), "]"
    ),
    across(c(ATT, SE), \(x) sprintf("%.3f", x))
  ) |>
  tt(caption = "Overall ATT — CIT cuts")
```

### Pre-trend diagnostics (CIT)

```{r}
#| label: tbl-did-cit-pretrend

bind_rows(
  extract_pretrend(did_results$cit_investments$event_study) |>
    mutate(outcome = "log(Investment)"),
  extract_pretrend(did_results$cit_employees$event_study) |>
    mutate(outcome = "log(Employment)")
) |>
  mutate(across(c(att, se, lower, upper), \(x) sprintf("%.4f", x))) |>
  select(Outcome = outcome, `Event time` = e, ATT = att, SE = se,
         Lower = lower, Upper = upper, Sig = sig) |>
  tt(caption = "Pre-treatment event-study coefficients (should be ~0 for parallel trends)")
```


## Personal Income Tax (PIT)

::: {#fig-did-pit layout-ncol=2}

```{r}
#| label: fig-did-pit-investments
#| fig-cap: "Investment"
did_plots$pit_investments
```

```{r}
#| label: fig-did-pit-employees
#| fig-cap: "Employment"
did_plots$pit_employees
```

Event-study: effect of PIT cuts on firm-level outcomes
:::

```{r}
#| label: tbl-did-pit-att

tibble(
  Outcome = c("log(Investment)", "log(Employment)"),
  ATT = c(
    did_results$pit_investments$overall$overall.att,
    did_results$pit_employees$overall$overall.att
  ),
  SE = c(
    did_results$pit_investments$overall$overall.se,
    did_results$pit_employees$overall$overall.se
  )
) |>
  mutate(
    `95% CI` = paste0(
      "[", sprintf("%.3f", ATT - 1.96 * SE), ", ",
      sprintf("%.3f", ATT + 1.96 * SE), "]"
    ),
    across(c(ATT, SE), \(x) sprintf("%.3f", x))
  ) |>
  tt(caption = "Overall ATT — PIT cuts")
```

### Pre-trend diagnostics (PIT)

```{r}
#| label: tbl-did-pit-pretrend

bind_rows(
  extract_pretrend(did_results$pit_investments$event_study) |>
    mutate(outcome = "log(Investment)"),
  extract_pretrend(did_results$pit_employees$event_study) |>
    mutate(outcome = "log(Employment)")
) |>
  mutate(across(c(att, se, lower, upper), \(x) sprintf("%.4f", x))) |>
  select(Outcome = outcome, `Event time` = e, ATT = att, SE = se,
         Lower = lower, Upper = upper, Sig = sig) |>
  tt(caption = "Pre-treatment event-study coefficients (should be ~0 for parallel trends)")
```


## Interpretation

<!-- Human: fill in interpretation after reviewing results.
     Key questions:
     - Do pre-trend coefficients support parallel trends?
     - Are overall ATTs economically meaningful?
     - How do CIT vs PIT effects compare? -->
