---
title: "Explore Orbis Data"
execute:
    echo: true
---


```{r}

rm(list = ls())
gc()

pacman::p_load(
    targets,
    tidyverse,
    labelled,
    here,
    tinytable
)

here::i_am("notebooks/explore_orbis.qmd")
tar_config_set(store = here("_targets"))

theme_set(theme_minimal())

```


## Inspect raw firm data

```{r}
orbis_raw <- tar_read(orbis_raw)
```

What variables are available?

```{r}
generate_dictionary(orbis_raw) |>
    tt()

```

---

In Diff-in-Diff settings, having accurate date representation is key for identifying causal effects. What coded date should be interpreted as the date of observation, for econometrics purposes?

```{r}
orbis_raw |>
    summarise(
        .by = c(CLOSDATE, RELDATE_SAS),
        n = n()
    ) |>
    ggplot(aes(x = CLOSDATE, y = RELDATE_SAS, size = n)) +
    geom_point(alpha = 0.5, color = "coral")
```


Save for a few odd cases, for all observations `CLOSDATE` < `RELDATE_SAS`.

What would these variables look within a single firm?

```{r}


malaysia_raw <- orbis_raw |>
    filter(CNTRYCDE == "MY")

malaysia_raw |>
    filter(OS_ID_NUMBER == first(OS_ID_NUMBER)) |>
    arrange(CLOSDATE) |>
    select(CLOSDATE, RELDATE_SAS) |>
    tt()

```


Within a firm, there is no variation of `RELDATE_SAS`; there's only yearly variation of `CLOSEDATE`. We'll construct the time variable from `CLOSEDATE`.


```{r}
#| layout-ncol: 2
orbis_raw |>
    mutate(month_day = day(CLOSDATE)) |>
    ggplot(aes(month_day)) +
    geom_histogram()

orbis_raw |>
    mutate(month = month(CLOSDATE)) |>
    ggplot(aes(month)) +
    geom_histogram()
```

Most `CLOSEDATE` events regard the last day of the month; but not all of them.

Most observations are end-of-year statements. There are very few monthly and (complete) quarterly observations. We should homogenize the dataset to yearly, taking the last available observation of the year.


```{r}
#| include: false
#| cache: false
rm(orbis_raw)
gc()
```

## Inspect cleaned firm data

The cleaned dataset takes the above observation into account, and also renames and keeps the relevant variables. It is a firm-year dataset.

```{r}
orbis_clean <- tar_read(orbis_clean)

malaysia <- orbis_clean |>
    filter(alpha2 == "MY")
```


```{r}

malaysia |>
    summarise(
        .by = c(close_date),
        firms = n_distinct(firm_id)
    ) |>
    ggplot(aes(close_date, firms)) +
    geom_col()

malaysia |>
    mutate(month = lubridate::month(close_date)) |>
    summarise(
        .by = c(month),
        firms = n_distinct(firm_id)
    ) |>
    ggplot(aes(factor(month), firms)) +
    geom_col()
```

Note that few firms report complete quarterly results in Malaysia. Fewer still report monthly results.

```{r}
malaysia |>
    mutate(
        year = year(close_date)
    ) |>
    summarise(
        .by = c(firm_id, year),
        n = n()
    ) |>
    ggplot(aes(n)) +
    geom_histogram()
```



```{r}

malaysia |>
    summarise(
        .by = c(firm_id),
        years_covered = n_distinct(close_date)

    ) |>
    ggplot(aes(years_covered)) +
    geom_histogram(binwidth = 1) +
    scale_x_continuous(breaks = seq(1, 17, 2))
```


```{r}
malaysia |>
    summarise(
        .by = year,
        firms = n_distinct(firm_id)
    ) |>
    ggplot(aes(year, firms)) +
    geom_col()
```




```{r}
malaysia |>
    summarise(
        .by = firm_id,
        years = n_distinct(close_date)
    ) |>
    ggplot(aes(years)) +
    geom_histogram(binwidth = 1)
```

We can merge at year-country level with the macro data we have. For DiD, it has to be balanced.