---
title: "Phase 1: Macro Local Projections"
---

```{r}
#| label: setup
#| cache: false
#| include: false

rm(list = ls())
gc()

pacman::p_load(
  targets,
  tidyverse,
  fixest,
  tinytable,
  here
)

here::i_am("notebooks/local_projections.qmd")
tar_config_set(store = here("_targets"))

# Source LP functions (for plot_irf helper)
source(here("R/local_projections.R"))

theme_set(theme_minimal(base_size = 13))

# Load targets
lp_cumulative <- tar_read(lp_cumulative)
lp_plots      <- tar_read(lp_plots)
lp_models     <- tar_read(lp_models)

# Outcome display names (shared across CIT/PIT)
outcome_labels <- c(
  gdppc           = "GDP pc",
  rev_tax         = "Tax revenue",
  tax_inc_prof_cp = "Income tax rev.",
  tax_inc_prof_id = "Income tax (indiv.)",
  pvt_investment  = "Pvt investment",
  fdi             = "FDI",
  consumption     = "Consumption"
)
```

```{r}
#| label: helpers
#| cache: false

build_summary_table <- function(tx_id, outcome_labels, lp_cumulative, lp_models) {
  block_ids <- paste0(tx_id, "_", names(outcome_labels))

  # Extract h=5 cumulative effects (EAP)
  cum <- bind_rows(lp_cumulative[block_ids], .id = "block") |>
    filter(horizon == 5, group == "EAP") |>
    mutate(across(c(coef, se), ~ .x * 100))

  coef_row <- cum$coef |> sprintf(fmt = "%.3f")
  se_row   <- cum$se   |> sprintf(fmt = "(%.3f)")

  # Extract fit stats from H5 models
  n_row   <- sapply(block_ids, \(b) fitstat(lp_models[[b]]$H5, ~n)[[1]])
  wr2_row <- sapply(block_ids, \(b) r2(lp_models[[b]]$H5, "wr2")) |>
    sprintf(fmt = "%.3f")

  tbl_df <- data.frame(
    ` ` = c("Coef (pp)", "", "N", "Within R\u00b2"),
    rbind(coef_row, se_row, n_row, wr2_row),
    check.names = FALSE,
    stringsAsFactors = FALSE
  )
  names(tbl_df) <- c(" ", unname(outcome_labels))

  tt(tbl_df) |>
    style_tt(i = 2, line = "b", line_color = "#d3d3d3")
}
```

## CIT Cuts

::: {#fig-cit-cut layout-ncol=2}

```{r}
#| label: fig-cit-cut-gdppc
#| fig-cap: "GDP per capita"
lp_plots$cit_cut_gdppc
```

```{r}
#| label: fig-cit-cut-rev-tax
#| fig-cap: "Tax revenue"
lp_plots$cit_cut_rev_tax
```

```{r}
#| label: fig-cit-cut-tax-inc-prof-cp
#| fig-cap: "Income tax revenue"
lp_plots$cit_cut_tax_inc_prof_cp
```

```{r}
#| label: fig-cit-cut-tax-inc-prof-id
#| fig-cap: "Income tax (indiv.)"
lp_plots$cit_cut_tax_inc_prof_id
```

```{r}
#| label: fig-cit-cut-pvt-investment
#| fig-cap: "Private investment"
lp_plots$cit_cut_pvt_investment
```

```{r}
#| label: fig-cit-cut-fdi
#| fig-cap: "FDI"
lp_plots$cit_cut_fdi
```

```{r}
#| label: fig-cit-cut-consumption
#| fig-cap: "Consumption"
lp_plots$cit_cut_consumption
```

Cumulative effect of a 1 pp CIT cut on selected outcomes (EAP)
:::

## CIT Hikes

::: {#fig-cit-hike layout-ncol=2}

```{r}
#| label: fig-cit-hike-gdppc
#| fig-cap: "GDP per capita"
lp_plots$cit_hike_gdppc
```

```{r}
#| label: fig-cit-hike-rev-tax
#| fig-cap: "Tax revenue"
lp_plots$cit_hike_rev_tax
```

```{r}
#| label: fig-cit-hike-tax-inc-prof-cp
#| fig-cap: "Income tax revenue"
lp_plots$cit_hike_tax_inc_prof_cp
```

```{r}
#| label: fig-cit-hike-tax-inc-prof-id
#| fig-cap: "Income tax (indiv.)"
lp_plots$cit_hike_tax_inc_prof_id
```

```{r}
#| label: fig-cit-hike-pvt-investment
#| fig-cap: "Private investment"
lp_plots$cit_hike_pvt_investment
```

```{r}
#| label: fig-cit-hike-fdi
#| fig-cap: "FDI"
lp_plots$cit_hike_fdi
```

```{r}
#| label: fig-cit-hike-consumption
#| fig-cap: "Consumption"
lp_plots$cit_hike_consumption
```

Cumulative effect of a 1 pp CIT hike on selected outcomes (EAP)
:::

## PIT Cuts

::: {#fig-pit-cut layout-ncol=2}

```{r}
#| label: fig-pit-cut-gdppc
#| fig-cap: "GDP per capita"
lp_plots$pit_cut_gdppc
```

```{r}
#| label: fig-pit-cut-rev-tax
#| fig-cap: "Tax revenue"
lp_plots$pit_cut_rev_tax
```

```{r}
#| label: fig-pit-cut-tax-inc-prof-cp
#| fig-cap: "Income tax revenue"
lp_plots$pit_cut_tax_inc_prof_cp
```

```{r}
#| label: fig-pit-cut-tax-inc-prof-id
#| fig-cap: "Income tax (indiv.)"
lp_plots$pit_cut_tax_inc_prof_id
```

```{r}
#| label: fig-pit-cut-pvt-investment
#| fig-cap: "Private investment"
lp_plots$pit_cut_pvt_investment
```

```{r}
#| label: fig-pit-cut-fdi
#| fig-cap: "FDI"
lp_plots$pit_cut_fdi
```

```{r}
#| label: fig-pit-cut-consumption
#| fig-cap: "Consumption"
lp_plots$pit_cut_consumption
```

Cumulative effect of a 1 pp PIT cut on selected outcomes (EAP)
:::

## PIT Hikes

::: {#fig-pit-hike layout-ncol=2}

```{r}
#| label: fig-pit-hike-gdppc
#| fig-cap: "GDP per capita"
lp_plots$pit_hike_gdppc
```

```{r}
#| label: fig-pit-hike-rev-tax
#| fig-cap: "Tax revenue"
lp_plots$pit_hike_rev_tax
```

```{r}
#| label: fig-pit-hike-tax-inc-prof-cp
#| fig-cap: "Income tax revenue"
lp_plots$pit_hike_tax_inc_prof_cp
```

```{r}
#| label: fig-pit-hike-tax-inc-prof-id
#| fig-cap: "Income tax (indiv.)"
lp_plots$pit_hike_tax_inc_prof_id
```

```{r}
#| label: fig-pit-hike-pvt-investment
#| fig-cap: "Private investment"
lp_plots$pit_hike_pvt_investment
```

```{r}
#| label: fig-pit-hike-fdi
#| fig-cap: "FDI"
lp_plots$pit_hike_fdi
```

```{r}
#| label: fig-pit-hike-consumption
#| fig-cap: "Consumption"
lp_plots$pit_hike_consumption
```

Cumulative effect of a 1 pp PIT hike on selected outcomes (EAP)
:::

## Summary

::: {#tbl-lp-5}

```{r}
#| label: tbl-cit-cut-summary
#| tbl-cap: "CIT Cuts"

build_summary_table("cit_cut", outcome_labels, lp_cumulative, lp_models)
```

```{r}
#| label: tbl-cit-hike-summary
#| tbl-cap: "CIT Hikes"

build_summary_table("cit_hike", outcome_labels, lp_cumulative, lp_models)
```

```{r}
#| label: tbl-pit-cut-summary
#| tbl-cap: "PIT Cuts"

build_summary_table("pit_cut", outcome_labels, lp_cumulative, lp_models)
```

```{r}
#| label: tbl-pit-hike-summary
#| tbl-cap: "PIT Hikes"

build_summary_table("pit_hike", outcome_labels, lp_cumulative, lp_models)
```

Cumulative effect of tax changes after 5 years (EAP)
:::


@tbl-lp-5 shows very few statistically significant coefficients. Most importantly, "first stage" coefficients (tax revenue, income tax revenue, and individual income tax revenue) are highly insignificant.

These results highlight the importance of using micro data to measure outcomes. Cuts and hikes are estimated separately to allow for asymmetric effects.

---



```{r}
#| label: appendix-results
#| results: asis
#| include: false

tx_labels <- c(cit_cut = "CIT Cut", cit_hike = "CIT Hike", pit_cut = "PIT Cut", pit_hike = "PIT Hike")

for (tx_id in names(lp_treatments())) {
  for (out_id in names(lp_outcomes())) {
    bid <- paste0(tx_id, "_", out_id)
    cat("\n\n## ", tx_labels[[tx_id]], " \u2014 ", outcome_labels[[out_id]], "\n\n")
    cat("::: {.panel-tabset}\n\n")

    for (g in c("MIC", "HIC")) {
      cat("### ", g, "\n\n")
      p <- plot_irf(lp_cumulative[[bid]], bid, group = g)
      print(p)
      cat("\n\n")
    }

    cat(":::\n\n")
  }
}
```
