---
title: "Phase 1: Macro Local Projections"
format:
  html:
    toc: true
    code-fold: true
execute:
  echo: false
  warning: false
---

```{r}
#| label: setup
#| cache: false

rm(list = ls())
gc()

pacman::p_load(
  targets,
  tidyverse,
  fixest,
  tinytable,
  here
)

here::i_am("notebooks/lp.qmd")
tar_config_set(store = here("_targets"))

# Source LP functions (for plot_irf helper)
source(here("R/local_projections.R"))

theme_set(theme_minimal(base_size = 13))

# Load targets
lp_cumulative <- tar_read(lp_cumulative)
lp_plots      <- tar_read(lp_plots)
lp_models     <- tar_read(lp_models)

# Outcome display names (shared across CIT/PIT)
outcome_labels <- c(
  gdppc           = "GDP pc",
  rev_tax         = "Tax revenue",
  tax_inc_prof_cp = "Income tax rev.",
  tax_inc_prof_id = "Income tax (indiv.)",
  pvt_investment  = "Pvt investment",
  fdi             = "FDI",
  consumption     = "Consumption"
)
```

```{r}
#| label: helpers
#| cache: false

build_summary_table <- function(tx_id, outcome_labels, lp_cumulative, lp_models) {
  block_ids <- paste0(tx_id, "_", names(outcome_labels))

  # Extract h=5 cumulative effects (EAP)
  cum <- bind_rows(lp_cumulative[block_ids], .id = "block") |>
    filter(horizon == 5, group == "EAP") |>
    mutate(across(c(coef, se), ~ .x * 100))

  coef_row <- cum$coef |> sprintf(fmt = "%.3f")
  se_row   <- cum$se   |> sprintf(fmt = "(%.3f)")

  # Extract fit stats from H5 models
  n_row   <- sapply(block_ids, \(b) fitstat(lp_models[[b]]$H5, ~n)[[1]])
  wr2_row <- sapply(block_ids, \(b) r2(lp_models[[b]]$H5, "wr2")) |>
    sprintf(fmt = "%.3f")

  tbl_df <- data.frame(
    ` ` = c("Coef (pp)", "", "N", "Within R\u00b2"),
    rbind(coef_row, se_row, n_row, wr2_row),
    check.names = FALSE,
    stringsAsFactors = FALSE
  )
  names(tbl_df) <- c(" ", unname(outcome_labels))

  tt(tbl_df) |>
    style_tt(i = 2, line = "b", line_color = "#d3d3d3")
}
```

## Corporate Income Tax (CIT)

::: {#fig-cit layout-ncol=2}

```{r}
#| label: fig-cit-gdppc
#| fig-cap: "GDP per capita"
lp_plots$cit_gdppc
```

```{r}
#| label: fig-cit-rev-tax
#| fig-cap: "Tax revenue"
lp_plots$cit_rev_tax
```

```{r}
#| label: fig-cit-tax-inc-prof-cp
#| fig-cap: "Income tax revenue"
lp_plots$cit_tax_inc_prof_cp
```

```{r}
#| label: fig-cit-tax-inc-prof-id
#| fig-cap: "Income tax (indiv.)"
lp_plots$cit_tax_inc_prof_id
```

```{r}
#| label: fig-cit-pvt-investment
#| fig-cap: "Private investment"
lp_plots$cit_pvt_investment
```

```{r}
#| label: fig-cit-fdi
#| fig-cap: "FDI"
lp_plots$cit_fdi
```

```{r}
#| label: fig-cit-consumption
#| fig-cap: "Consumption"
lp_plots$cit_consumption
```

Cumulative effect of a 1 pp CIT cut on selected outcomes (EAP)
:::

## Personal Income Tax (PIT)

::: {#fig-pit layout-ncol=2}

```{r}
#| label: fig-pit-gdppc
#| fig-cap: "GDP per capita"
lp_plots$pit_gdppc
```

```{r}
#| label: fig-pit-rev-tax
#| fig-cap: "Tax revenue"
lp_plots$pit_rev_tax
```

```{r}
#| label: fig-pit-tax-inc-prof-cp
#| fig-cap: "Income tax revenue"
lp_plots$pit_tax_inc_prof_cp
```

```{r}
#| label: fig-pit-tax-inc-prof-id
#| fig-cap: "Income tax (indiv.)"
lp_plots$pit_tax_inc_prof_id
```

```{r}
#| label: fig-pit-pvt-investment
#| fig-cap: "Private investment"
lp_plots$pit_pvt_investment
```

```{r}
#| label: fig-pit-fdi
#| fig-cap: "FDI"
lp_plots$pit_fdi
```

```{r}
#| label: fig-pit-consumption
#| fig-cap: "Consumption"
lp_plots$pit_consumption
```

Cumulative effect of a 1 pp PIT cut on selected outcomes (EAP)
:::

## Summary

::: {#tbl-lp-5}

```{r}
#| label: tbl-cit-summary
#| tbl-cap: "Corporate Income Tax cuts"

build_summary_table("cit", outcome_labels, lp_cumulative, lp_models)
```

```{r}
#| label: tbl-pit-summary
#| tbl-cap: "Personal Income Tax Cuts"

build_summary_table("pit", outcome_labels, lp_cumulative, lp_models)
```

Cumulative effect of tax cuts after 5 years (EAP)
:::


@tbl-lp-5 shows very few statistically significant coefficients. Most importantly, "first stage" coefficients (tax revenue, income tax revenue, and individual income tax revenue) are highly insignificant.

These results highlight the importance of using micro data to measure outcomes. 

---

# Appendix: MIC and HIC Results {.appendix}

```{r}
#| label: appendix-results
#| results: asis

tx_labels <- c(cit = "CIT", pit = "PIT")

for (tx_id in names(lp_treatments())) {
  for (out_id in names(lp_outcomes())) {
    bid <- paste0(tx_id, "_", out_id)
    cat("\n\n## ", tx_labels[[tx_id]], " \u2014 ", outcome_labels[[out_id]], "\n\n")
    cat("::: {.panel-tabset}\n\n")

    for (g in c("MIC", "HIC")) {
      cat("### ", g, "\n\n")
      p <- plot_irf(lp_cumulative[[bid]], bid, group = g)
      print(p)
      cat("\n\n")
    }

    cat(":::\n\n")
  }
}
```
