---
title: "Firm-Level Local Projections"
execute:
  cache: true
---

```{r}
#| label: setup
#| cache: false
#| include: false

rm(list = ls())
gc()

pacman::p_load(
  targets,
  tidyverse,
  fixest,
  tinytable,
  here
)

here::i_am("notebooks/lp_firms.qmd")
tar_config_set(store = here("_targets"))

tar_source(files = here("R"))

theme_set(theme_minimal(base_size = 13))


# Load targets
lp_firm_cumulative <- tar_read(lp_firm_cumulative)
lp_firm_plots      <- tar_read(lp_firm_plots)
lp_firm_summaries  <- tar_read(lp_firm_results)$summaries

# Outcome display labels (shared across CIT/PIT)
outcome_labels <- c(
  income_tax          = "Income Tax Payable",
  income_taxes        = "Income Taxes",
  social_expenditure  = "Social Exp.",
  revenues            = "Revenue",
  employees           = "Employment",
  investments         = "Investment",
  net_profit          = "Net Profit",
  total_assets        = "Total Assets",
  profit_per_employee = "Profit/Employee"
)
```

```{r}
#| label: helpers
#| cache: false

build_firm_summary_table <- function(tx_id, outcome_labels, lp_firm_cumulative, lp_firm_summaries) {
  block_ids <- paste0(tx_id, "_", names(outcome_labels))

  # h=5 cumulative effects for EAP
  cum <- bind_rows(lp_firm_cumulative[block_ids], .id = "block") |>
    filter(horizon == 5, group == "EAP") |>
    mutate(across(c(coef, se), ~ .x * 100))

  coef_row <- cum$coef |> sprintf(fmt = "%.3f")
  se_row   <- cum$se   |> sprintf(fmt = "(%.3f)")

  # Fit stats from pre-extracted summaries
  n_row   <- sapply(block_ids, \(b) lp_firm_summaries[[b]]$n)
  wr2_row <- sapply(block_ids, \(b) lp_firm_summaries[[b]]$wr2) |>
    sprintf(fmt = "%.3f")

  tbl_df <- data.frame(
    ` ` = c("Coef (pp)", "", "N", "Within R\u00b2"),
    rbind(coef_row, se_row, n_row, wr2_row),
    check.names = FALSE,
    stringsAsFactors = FALSE
  )
  names(tbl_df) <- c(" ", unname(outcome_labels))

  tt(tbl_df) |>
    style_tt(i = 2, line = "b", line_color = "#d3d3d3")
}
```

## CIT Cuts

::: {#fig-firm-cit-cut layout-ncol=2}

```{r}
#| label: fig-firm-cit-cut-income-tax
#| fig-cap: "Income Tax Payable"
lp_firm_plots$cit_cut_income_tax
```

```{r}
#| label: fig-firm-cit-cut-income-taxes
#| fig-cap: "Income Taxes"
lp_firm_plots$cit_cut_income_taxes
```

```{r}
#| label: fig-firm-cit-cut-social-expenditure
#| fig-cap: "Social Expenditure"
lp_firm_plots$cit_cut_social_expenditure
```

```{r}
#| label: fig-firm-cit-cut-revenues
#| fig-cap: "Revenue"
lp_firm_plots$cit_cut_revenues
```

```{r}
#| label: fig-firm-cit-cut-employees
#| fig-cap: "Employment"
lp_firm_plots$cit_cut_employees
```

```{r}
#| label: fig-firm-cit-cut-investments
#| fig-cap: "Investment"
lp_firm_plots$cit_cut_investments
```

```{r}
#| label: fig-firm-cit-cut-net-profit
#| fig-cap: "Net Profit"
lp_firm_plots$cit_cut_net_profit
```

```{r}
#| label: fig-firm-cit-cut-total-assets
#| fig-cap: "Total Assets"
lp_firm_plots$cit_cut_total_assets
```

```{r}
#| label: fig-firm-cit-cut-profit-per-employee
#| fig-cap: "Profit per Employee"
lp_firm_plots$cit_cut_profit_per_employee
```

Cumulative effect of a 1 pp CIT cut on firm-level outcomes (EAP)
:::

## CIT Hikes

::: {#fig-firm-cit-hike layout-ncol=2}

```{r}
#| label: fig-firm-cit-hike-income-tax
#| fig-cap: "Income Tax Payable"
lp_firm_plots$cit_hike_income_tax
```

```{r}
#| label: fig-firm-cit-hike-income-taxes
#| fig-cap: "Income Taxes"
lp_firm_plots$cit_hike_income_taxes
```

```{r}
#| label: fig-firm-cit-hike-social-expenditure
#| fig-cap: "Social Expenditure"
lp_firm_plots$cit_hike_social_expenditure
```

```{r}
#| label: fig-firm-cit-hike-revenues
#| fig-cap: "Revenue"
lp_firm_plots$cit_hike_revenues
```

```{r}
#| label: fig-firm-cit-hike-employees
#| fig-cap: "Employment"
lp_firm_plots$cit_hike_employees
```

```{r}
#| label: fig-firm-cit-hike-investments
#| fig-cap: "Investment"
lp_firm_plots$cit_hike_investments
```

```{r}
#| label: fig-firm-cit-hike-net-profit
#| fig-cap: "Net Profit"
lp_firm_plots$cit_hike_net_profit
```

```{r}
#| label: fig-firm-cit-hike-total-assets
#| fig-cap: "Total Assets"
lp_firm_plots$cit_hike_total_assets
```

```{r}
#| label: fig-firm-cit-hike-profit-per-employee
#| fig-cap: "Profit per Employee"
lp_firm_plots$cit_hike_profit_per_employee
```

Cumulative effect of a 1 pp CIT hike on firm-level outcomes (EAP)
:::

## PIT Cuts

::: {#fig-firm-pit-cut layout-ncol=2}

```{r}
#| label: fig-firm-pit-cut-income-tax
#| fig-cap: "Income Tax Payable"
lp_firm_plots$pit_cut_income_tax
```

```{r}
#| label: fig-firm-pit-cut-income-taxes
#| fig-cap: "Income Taxes"
lp_firm_plots$pit_cut_income_taxes
```

```{r}
#| label: fig-firm-pit-cut-social-expenditure
#| fig-cap: "Social Expenditure"
lp_firm_plots$pit_cut_social_expenditure
```

```{r}
#| label: fig-firm-pit-cut-revenues
#| fig-cap: "Revenue"
lp_firm_plots$pit_cut_revenues
```

```{r}
#| label: fig-firm-pit-cut-employees
#| fig-cap: "Employment"
lp_firm_plots$pit_cut_employees
```

```{r}
#| label: fig-firm-pit-cut-investments
#| fig-cap: "Investment"
lp_firm_plots$pit_cut_investments
```

```{r}
#| label: fig-firm-pit-cut-net-profit
#| fig-cap: "Net Profit"
lp_firm_plots$pit_cut_net_profit
```

```{r}
#| label: fig-firm-pit-cut-total-assets
#| fig-cap: "Total Assets"
lp_firm_plots$pit_cut_total_assets
```

```{r}
#| label: fig-firm-pit-cut-profit-per-employee
#| fig-cap: "Profit per Employee"
lp_firm_plots$pit_cut_profit_per_employee
```

Cumulative effect of a 1 pp PIT cut on firm-level outcomes (EAP)
:::

## PIT Hikes

::: {#fig-firm-pit-hike layout-ncol=2}

```{r}
#| label: fig-firm-pit-hike-income-tax
#| fig-cap: "Income Tax Payable"
lp_firm_plots$pit_hike_income_tax
```

```{r}
#| label: fig-firm-pit-hike-income-taxes
#| fig-cap: "Income Taxes"
lp_firm_plots$pit_hike_income_taxes
```

```{r}
#| label: fig-firm-pit-hike-social-expenditure
#| fig-cap: "Social Expenditure"
lp_firm_plots$pit_hike_social_expenditure
```

```{r}
#| label: fig-firm-pit-hike-revenues
#| fig-cap: "Revenue"
lp_firm_plots$pit_hike_revenues
```

```{r}
#| label: fig-firm-pit-hike-employees
#| fig-cap: "Employment"
lp_firm_plots$pit_hike_employees
```

```{r}
#| label: fig-firm-pit-hike-investments
#| fig-cap: "Investment"
lp_firm_plots$pit_hike_investments
```

```{r}
#| label: fig-firm-pit-hike-net-profit
#| fig-cap: "Net Profit"
lp_firm_plots$pit_hike_net_profit
```

```{r}
#| label: fig-firm-pit-hike-total-assets
#| fig-cap: "Total Assets"
lp_firm_plots$pit_hike_total_assets
```

```{r}
#| label: fig-firm-pit-hike-profit-per-employee
#| fig-cap: "Profit per Employee"
lp_firm_plots$pit_hike_profit_per_employee
```

Cumulative effect of a 1 pp PIT hike on firm-level outcomes (EAP)
:::

## Summary

::: {#tbl-firm-lp-5}

```{r}
#| label: tbl-firm-cit-cut-summary
#| tbl-cap: "CIT Cuts"

build_firm_summary_table("cit_cut", outcome_labels, lp_firm_cumulative, lp_firm_summaries)
```

```{r}
#| label: tbl-firm-cit-hike-summary
#| tbl-cap: "CIT Hikes"

build_firm_summary_table("cit_hike", outcome_labels, lp_firm_cumulative, lp_firm_summaries)
```

```{r}
#| label: tbl-firm-pit-cut-summary
#| tbl-cap: "PIT Cuts"

build_firm_summary_table("pit_cut", outcome_labels, lp_firm_cumulative, lp_firm_summaries)
```

```{r}
#| label: tbl-firm-pit-hike-summary
#| tbl-cap: "PIT Hikes"

build_firm_summary_table("pit_hike", outcome_labels, lp_firm_cumulative, lp_firm_summaries)
```

Cumulative effect of tax changes on firm-level outcomes after 5 years (EAP)
:::

## Regional Comparison

### CIT Cuts

::: {#fig-firm-cit-cut-regional layout-ncol=2}

```{r}
#| label: fig-firm-cit-cut-regional-income-tax
#| fig-cap: "Income Tax Payable"
plot_lp_firm_irf_faceted(lp_firm_cumulative$cit_cut_income_tax, "cit_cut_income_tax")
```

```{r}
#| label: fig-firm-cit-cut-regional-income-taxes
#| fig-cap: "Income Taxes"
plot_lp_firm_irf_faceted(lp_firm_cumulative$cit_cut_income_taxes, "cit_cut_income_taxes")
```

```{r}
#| label: fig-firm-cit-cut-regional-social-expenditure
#| fig-cap: "Social Expenditure"
plot_lp_firm_irf_faceted(lp_firm_cumulative$cit_cut_social_expenditure, "cit_cut_social_expenditure")
```

```{r}
#| label: fig-firm-cit-cut-regional-revenues
#| fig-cap: "Revenue"
plot_lp_firm_irf_faceted(lp_firm_cumulative$cit_cut_revenues, "cit_cut_revenues")
```

```{r}
#| label: fig-firm-cit-cut-regional-employees
#| fig-cap: "Employment"
plot_lp_firm_irf_faceted(lp_firm_cumulative$cit_cut_employees, "cit_cut_employees")
```

```{r}
#| label: fig-firm-cit-cut-regional-investments
#| fig-cap: "Investment"
plot_lp_firm_irf_faceted(lp_firm_cumulative$cit_cut_investments, "cit_cut_investments")
```

```{r}
#| label: fig-firm-cit-cut-regional-net-profit
#| fig-cap: "Net Profit"
plot_lp_firm_irf_faceted(lp_firm_cumulative$cit_cut_net_profit, "cit_cut_net_profit")
```

```{r}
#| label: fig-firm-cit-cut-regional-total-assets
#| fig-cap: "Total Assets"
plot_lp_firm_irf_faceted(lp_firm_cumulative$cit_cut_total_assets, "cit_cut_total_assets")
```

```{r}
#| label: fig-firm-cit-cut-regional-profit-per-employee
#| fig-cap: "Profit per Employee"
plot_lp_firm_irf_faceted(lp_firm_cumulative$cit_cut_profit_per_employee, "cit_cut_profit_per_employee")
```

Cumulative effect of a 1 pp CIT cut by region (EAP, MIC, HIC)
:::

### CIT Hikes

::: {#fig-firm-cit-hike-regional layout-ncol=2}

```{r}
#| label: fig-firm-cit-hike-regional-income-tax
#| fig-cap: "Income Tax Payable"
plot_lp_firm_irf_faceted(lp_firm_cumulative$cit_hike_income_tax, "cit_hike_income_tax")
```

```{r}
#| label: fig-firm-cit-hike-regional-income-taxes
#| fig-cap: "Income Taxes"
plot_lp_firm_irf_faceted(lp_firm_cumulative$cit_hike_income_taxes, "cit_hike_income_taxes")
```

```{r}
#| label: fig-firm-cit-hike-regional-social-expenditure
#| fig-cap: "Social Expenditure"
plot_lp_firm_irf_faceted(lp_firm_cumulative$cit_hike_social_expenditure, "cit_hike_social_expenditure")
```

```{r}
#| label: fig-firm-cit-hike-regional-revenues
#| fig-cap: "Revenue"
plot_lp_firm_irf_faceted(lp_firm_cumulative$cit_hike_revenues, "cit_hike_revenues")
```

```{r}
#| label: fig-firm-cit-hike-regional-employees
#| fig-cap: "Employment"
plot_lp_firm_irf_faceted(lp_firm_cumulative$cit_hike_employees, "cit_hike_employees")
```

```{r}
#| label: fig-firm-cit-hike-regional-investments
#| fig-cap: "Investment"
plot_lp_firm_irf_faceted(lp_firm_cumulative$cit_hike_investments, "cit_hike_investments")
```

```{r}
#| label: fig-firm-cit-hike-regional-net-profit
#| fig-cap: "Net Profit"
plot_lp_firm_irf_faceted(lp_firm_cumulative$cit_hike_net_profit, "cit_hike_net_profit")
```

```{r}
#| label: fig-firm-cit-hike-regional-total-assets
#| fig-cap: "Total Assets"
plot_lp_firm_irf_faceted(lp_firm_cumulative$cit_hike_total_assets, "cit_hike_total_assets")
```

```{r}
#| label: fig-firm-cit-hike-regional-profit-per-employee
#| fig-cap: "Profit per Employee"
plot_lp_firm_irf_faceted(lp_firm_cumulative$cit_hike_profit_per_employee, "cit_hike_profit_per_employee")
```

Cumulative effect of a 1 pp CIT hike by region (EAP, MIC, HIC)
:::

### PIT Cuts

::: {#fig-firm-pit-cut-regional layout-ncol=2}

```{r}
#| label: fig-firm-pit-cut-regional-income-tax
#| fig-cap: "Income Tax Payable"
plot_lp_firm_irf_faceted(lp_firm_cumulative$pit_cut_income_tax, "pit_cut_income_tax")
```

```{r}
#| label: fig-firm-pit-cut-regional-income-taxes
#| fig-cap: "Income Taxes"
plot_lp_firm_irf_faceted(lp_firm_cumulative$pit_cut_income_taxes, "pit_cut_income_taxes")
```

```{r}
#| label: fig-firm-pit-cut-regional-social-expenditure
#| fig-cap: "Social Expenditure"
plot_lp_firm_irf_faceted(lp_firm_cumulative$pit_cut_social_expenditure, "pit_cut_social_expenditure")
```

```{r}
#| label: fig-firm-pit-cut-regional-revenues
#| fig-cap: "Revenue"
plot_lp_firm_irf_faceted(lp_firm_cumulative$pit_cut_revenues, "pit_cut_revenues")
```

```{r}
#| label: fig-firm-pit-cut-regional-employees
#| fig-cap: "Employment"
plot_lp_firm_irf_faceted(lp_firm_cumulative$pit_cut_employees, "pit_cut_employees")
```

```{r}
#| label: fig-firm-pit-cut-regional-investments
#| fig-cap: "Investment"
plot_lp_firm_irf_faceted(lp_firm_cumulative$pit_cut_investments, "pit_cut_investments")
```

```{r}
#| label: fig-firm-pit-cut-regional-net-profit
#| fig-cap: "Net Profit"
plot_lp_firm_irf_faceted(lp_firm_cumulative$pit_cut_net_profit, "pit_cut_net_profit")
```

```{r}
#| label: fig-firm-pit-cut-regional-total-assets
#| fig-cap: "Total Assets"
plot_lp_firm_irf_faceted(lp_firm_cumulative$pit_cut_total_assets, "pit_cut_total_assets")
```

```{r}
#| label: fig-firm-pit-cut-regional-profit-per-employee
#| fig-cap: "Profit per Employee"
plot_lp_firm_irf_faceted(lp_firm_cumulative$pit_cut_profit_per_employee, "pit_cut_profit_per_employee")
```

Cumulative effect of a 1 pp PIT cut by region (EAP, MIC, HIC)
:::

### PIT Hikes

::: {#fig-firm-pit-hike-regional layout-ncol=2}

```{r}
#| label: fig-firm-pit-hike-regional-income-tax
#| fig-cap: "Income Tax Payable"
plot_lp_firm_irf_faceted(lp_firm_cumulative$pit_hike_income_tax, "pit_hike_income_tax")
```

```{r}
#| label: fig-firm-pit-hike-regional-income-taxes
#| fig-cap: "Income Taxes"
plot_lp_firm_irf_faceted(lp_firm_cumulative$pit_hike_income_taxes, "pit_hike_income_taxes")
```

```{r}
#| label: fig-firm-pit-hike-regional-social-expenditure
#| fig-cap: "Social Expenditure"
plot_lp_firm_irf_faceted(lp_firm_cumulative$pit_hike_social_expenditure, "pit_hike_social_expenditure")
```

```{r}
#| label: fig-firm-pit-hike-regional-revenues
#| fig-cap: "Revenue"
plot_lp_firm_irf_faceted(lp_firm_cumulative$pit_hike_revenues, "pit_hike_revenues")
```

```{r}
#| label: fig-firm-pit-hike-regional-employees
#| fig-cap: "Employment"
plot_lp_firm_irf_faceted(lp_firm_cumulative$pit_hike_employees, "pit_hike_employees")
```

```{r}
#| label: fig-firm-pit-hike-regional-investments
#| fig-cap: "Investment"
plot_lp_firm_irf_faceted(lp_firm_cumulative$pit_hike_investments, "pit_hike_investments")
```

```{r}
#| label: fig-firm-pit-hike-regional-net-profit
#| fig-cap: "Net Profit"
plot_lp_firm_irf_faceted(lp_firm_cumulative$pit_hike_net_profit, "pit_hike_net_profit")
```

```{r}
#| label: fig-firm-pit-hike-regional-total-assets
#| fig-cap: "Total Assets"
plot_lp_firm_irf_faceted(lp_firm_cumulative$pit_hike_total_assets, "pit_hike_total_assets")
```

```{r}
#| label: fig-firm-pit-hike-regional-profit-per-employee
#| fig-cap: "Profit per Employee"
plot_lp_firm_irf_faceted(lp_firm_cumulative$pit_hike_profit_per_employee, "pit_hike_profit_per_employee")
```

Cumulative effect of a 1 pp PIT hike by region (EAP, MIC, HIC)
:::
