---
title: "Research Report"
author: "Your Name"
date: today
format:
  html:
    toc: true
    code-fold: true
  pdf:
    toc: true
execute:
  echo: true
  warning: false
---

## Introduction

This is a template Quarto document for your research project. It integrates with the `targets` pipeline for reproducible analysis.

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(targets)
library(here)
```

## Load Pipeline Results

Use `tar_read()` to load objects from your targets pipeline:

```{r}
#| label: load-results
#| eval: false

# Example: Load cleaned data from the pipeline
# clean_data <- tar_read(clean_data)

# Example: Load model results
# model <- tar_read(model)
```

## Analysis

Add your analysis code here. Reference outputs from the targets pipeline to ensure reproducibility.

```{r}
#| label: example-plot
#| fig-cap: "Example visualization"

# Example plot using mtcars (replace with your data)
mtcars |>
  ggplot(aes(x = wt, y = mpg, color = factor(cyl))) +
  geom_point(size = 3) +
  labs(
    title = "Fuel Efficiency by Weight",
    x = "Weight (1000 lbs)",
    y = "Miles per Gallon",
    color = "Cylinders"
  ) +
  theme_minimal()
```

## Results

Summarize your findings here.

## References

Add your references here or use a `.bib` file with Quarto's citation system.
